\section{Construction \& Implementation Details}

In this section, we discuss the construction and implementation details 
of the suggested SPV style sync committee based light client. Note that the details of 
the contruction are not final and are subject to change.

The client will be implemented as a Go cosmos module. On a high level, the new
construction would work as follows:
\begin{enumerate}
    \item A user initiates the bridge transfer by sending a transaction to a
        designated smart contract on the Ethereum (source) chain, similar to
        the existing construction.
    \item A (possibly different) user then submits a request on the Axelar
        network with the corresponding Ethereum transaction's hash.
    \item Axelar attestors then query the full node to check if the Ethereum
        transaction is finalized; if so, they generate a light client proof with
        two components: (i) a consensus verification proof; (ii) an
        execution verification proof.
    \item A user submits the attestors' proof on the Axelar (destination)
        chain.
    \item The proof is verified on-chain by the Axelar full nodes; if the proof
        is valid, the transaction is executed on the Axelar chain.
\end{enumerate}

The client module will consist of two main components: Consensus Verification
and Execution Verification.

\subsection{Consensus Verification}

This module is responsible for keeping track of the latest finalized block and
the latest sync committee. Using this information, it is used to generate and
validate consensus verification proofs. These proofs mainly include aggregate
sync committee signatures and are of two types:
\begin{itemize}
    \item \textbf{Update Latest Sync Committee.} This proof validates the sync
        committee handover, that is updating the committee from one period to
        the next. It can be generated using Ethereum's beacon chain API,\footnote{\url{https://ethereum.github.io/beacon-APIs}}
        specifically the endpoint\\
        \texttt{/eth/v1/beacon/light\_client/updates}.
        The proof's verification involves checking the BLS aggregate signature
        of the sync committee and the Merkle inclusion proof of the next sync
        committee to the signed header.
    \item \textbf{Update Latest Finalized Block} This proof allows for updating
        the latest finalized block. It can be generated using the beacon chain
        API endpoint\\\texttt{/eth/v1/beacon/light\_client/finality\_update}.
        Its verification involves checking the BLS aggregate signatures of the
        latest sync committee on the latest finalized block.
\end{itemize}

\subsection{Execution Verification}

This component is responsible for generating and verifying the execution
verification proof. We note that the scope of this grant proposal includes only
verifying if a transaction is included in a block or a certain event was
released from by a smart contract. 

The execution proof mainly constitutes of a Merkle inclusion proof of the
relevant transaction or event to the finalized block header received from the
consensus verification component. The proof is generated by fetching the
complete block, which contains all the transactions and events, and generating
the Merkle inclusion proof. Following, the proof verification is a
straightforward Merkle inclusion check.
